Lens Modeling in \sw

### 2013-12-12 text/tex/outlook.tex
editing text

\section{Extensions needed} \label{sec:todo}

@@

Lenses with more than one maximum can be allowed for.  See Figure 5c
in \citep{2001ApJ...557..594R} and Figure 4b in
\cite{2003ApJ...590...39K}.

Supply several images from several bands.

>>>>

\section{Outlook} \label{sec:todo}

The lens-modelling challenge indicates that the Spacewarps collective
is good, not only for identifying lens candidates for follow-up, but
modelling candidates as well.

There is, however, plenty of room for improvement.

First, the particular modelling strategy implemented is not the only
one possible.  \spl requires modellers to characterise the overall
image structure in abstract terms based on Fermat's principle, and the
placement of a mass distributions is done by the computer.  In other
modelling tools, the user puts down a trial mass distribution and has
the machine refine it.  A few of these modelling programs have also
been designed with citizen science in mind, and would be interesting
the in Spacewarps environment.

Second, \spl needs some enhancements.

One, model the source as well.

Another, lenses with more than one maximum can be allowed for.  See
Figure 5c in \citep{2001ApJ...557..594R} and Figure 4b in
\cite{2003ApJ...590...39K}.

Other modelling approaches also possible.

@@

### 2013-12-12 text/tex/results.tex

The modellers proffered a total of 129 models for the 29 sims in the
challenge.  Figures \ref{fig:6941} to \ref{fig:6915} show eight of
models in some detail.

@@

@@

Figure \ref{fig:6990} shows a long-axis quad.

Figure \ref{fig:6919} shows a short-axis quad.

Figure \ref{fig:6915} shows an inclined quad.

@@

>>>>

The modellers proffered a total of 129 models for the 29 sims in the
challenge.  Figures \ref{fig:6941} to \ref{fig:6919} show eight of
models in some detail.

@@

Figure \ref{fig:6990} shows an example of an arc that has split into
three images.  This kind of configuration, with a counter-image close
to the lensing galaxy and a more distant arc/triplet on the other
side, generically arises from an elongated mass distribution when the
source is displaced along the elongated direction.

Figure \ref{fig:6915} shows another quad.  This kind of configuration
arises when the mass is elongated and the source is displaced at an
angle to the elongation.

@@

To conclude this set of examples, Figure \ref{fig:6919} shows another
type of quad.  Actually, in this case the brightest part of the source
is only doubly imaged, but the source extends into a region that
produces four images.  We can also see from the real arrival-time
surface that a point source is a double on the verge of splitting into
a quad.  The modeller interpreted the system as a quad.  The
appearance of the arcs, shown in the bottom panel of Figure
\ref{fig:input-spag}, looks like an arc and counter-image such as
discussed with Figure \ref{fig:6990} above.  But there is an important
difference: the long arc is closer to the galaxy, as if the arc and
counter-image have swapped roles.  This configuration arises if the
source displacement is perpendicular to the long axis of the lensing
mass.

@@

The second test T2 was to compare the desired results of a modeling process, the mass distribution of the lens $\kappa(x, y)$.
To get a means of comparing the simulated data (sims) to the generated modeled data (models), the total convergence, also called enclosed mass $\kappa_{\text{encl}}(r)$ for both was calculated.
The Einstein radius $\Theta_E$ is defined by $\kappa_{\text{encl}}(\Theta_E)=1$ and gives a number that allows the comparison between the sims and the models.
We also let an expert model three selected systems to compare the results from volunteers to those of a professional.
